Peer Assignment 1
========================================================
Load the data

```{r echo = TRUE}
df = read.csv('activity.csv', header = T)
```

Aggregate data based on the date

```{r echo = TRUE}
df$date = as.Date(df$date, '%Y-%m-%d')
group_day = with(df, aggregate(df$steps, data.frame(df$date),sum))
```

Make a histogram of the total number of steps taken each day 

```{r echo = TRUE}
library(ggplot2)
ggplot(group_day[!is.na(group_day$x), ], aes(x = x)) + geom_histogram() + theme_bw() + ggtitle("Histogram of Total Steps Taken Each Day") + labs(x = 'Steps Taken Each Day')
```

Calculate the mean and median total number of steps taken per day

```{r echo = TRUE}
mean(group_day$x, na.rm = T)
median(group_day$x, na.rm = T)
```

Aggredate data based on the time interval

```{r echo = TRUE}
group_interval = with(df, aggregate(df$steps, data.frame(df$interval), function(x) mean(x,na.rm = T)))
```

Time series plot of 5-minute interval and the average number of steps taken, averaged accross all days

```{r echo = TRUE}
ggplot(group_interval) + geom_line(aes(x = df.interval, y = x)) + theme_bw() + ggtitle("Time Series Plot of 5-Minute Interval") + labs(x = '5-Minute Interval', y = 'Average Accross All Days')
```

Find out which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps
```{r echo = TRUE}
group_interval$df.interval[group_interval$x == max(group_interval$x)]
```

Number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r echo = TRUE}
sum(!complete.cases(df))
```

Filling in all of the missing values in the dataset with the mean for that 5-minute interval
```{r echo = TRUE}
names(group_interval) = c('interval', 'steps_mean')  
library(plyr)
temp = join(df[is.na(df$steps),], group_interval, by = 'interval', type = 'left')

```

Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r echo = TRUE}
newdf = df
newdf$steps[is.na(newdf$steps)] = temp$steps_mean
```

Histogram of the total number of steps taken each day
```{r echo = TRUE}
group_day_2 = with(newdf, aggregate(newdf$steps, data.frame(newdf$date),sum))
ggplot(group_day_2, aes(x = x)) + geom_histogram() + theme_bw() + ggtitle("Histogram of Total Steps Taken Each Day") + labs(x = 'Steps Taken Each Day')
```

Calculate the mean and median total number of steps taken per day
```{r echo = TRUE}
mean(group_day_2$x)
median(group_day_2$x)
```

The medain of steps taken each day increases by 1, while the mean remains the same. Inputing missing data with the mean of 5-minute interval sum don't have a big impact of the previous estimate. 

Create a new factor variable in the dataset with two levels – “weekday” and “weekend”
```{r echo = TRUE}
newdf$day = as.factor(weekdays(newdf$date))
levels(newdf$day)[levels(newdf$day) == 'Saturday' | levels(newdf$day) == 'Sunday'] = "weekend"
levels(newdf$day)[levels(newdf$day) != 'weekend'] = 'weekday'
```

Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). 
```{r echo = TRUE}
group_weekday = with(newdf, aggregate(newdf$steps, data.frame(newdf$interval, newdf$day),sum))
ggplot(group_weekday) + geom_line(aes(x = newdf.interval, y = x)) + facet_grid(.~newdf.day)+ theme_bw() + ggtitle("Time Series Plot of 5-Minute Interval (weekday/weekend)") + labs(x = '5-Minute Interval', y = 'Average Number of Steps Accross All Days')
```






